Meritocracy and distributive preferences ISSP

### 2020-08-26 production/prod_analysis-b.rmd
likert etiquetas y centrado

htmlreg(list(results_0_redist,results_0_accum), 
        caption = "null model of redistribution preferences and accumulation preferences", 
        custom.model.names = c("Redistribution", "Accumulation"), 
        caption.adove = T, star.symbol = "\\*")

@@

```{r results='asis'} 
htmlreg(list(results_1_redist__1, results_1_redist_3,results_1_redist_4,results_1_redist_5,results_1_redist_6,results_1_redist_7, results_1_redist_9, results_2_redist_macro_bv, results_3_redist_macro_bvi),
        caption = "Redistribution preference models", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "GINI x Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

@@

```{r results='asis'}
htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_nocong, results_3_accum_macro_bvi, results_3_accum_macro_bvi_nocong), 
        caption = "Comparison model excludig countries non convergent in the measurement", 
        custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), 
        custom.header = list("Redistribution" = 1:2, "Accumulation" = 3:4), 
        star.symbol = "\\*", 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> countries non convergent in the measurement model:Venezuela, Croatia, Cyprus, Italy, Latvia", 
        custom.coef.names = c("Intercept", "University. Ed.", "Quintile 2", "Quintile 3", "Quintile 4","Quintile 5", "Quintile miss", "Subjetive status", 
                              "Subjetive upward mobility", "Supjetive downward mobility","Subjetive non-mobility","Gender", "Age", "Meritorcatic perception", 
                              "Meritocratic preferences", "Unmeritocratic perception", "Unmeritocratic preferences", "Gini index", "Economic freedom index", 
                              "Merit-perception x Gini", "Merit-perception x Economic-freedom"), 
        caption.above = T)
```

@@

plota <- plot(estex.m23_2a, which="cook",
              cutoff = .1, sort = TRUE,
              xlab = "Cooks Distance Redistribution Model",
              ylab="Contries")

@@

```{r results='asis'}
htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_sininf,results_3_accum_macro_bvi, results_3_accum_macro_bvi_sininfl), 
        caption = "Comparison model Without influential cases in level two", 
        custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), 
        custom.header = list("Redistribution" = 1:2, "Accumulation" = 3:4), 
        caption.above = T, 
        star.symbol = "\\*", 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Influential contries: CYP, TUR, TWN, UKR,CZE, FRA, AUS, DNK, USA, VEN,PHL, POL, CHN, ISR, CHL, LVA, PHL", 
        custom.coef.names = c("Intercept", "University. Ed.", "Quintile 2", "Quintile 3", "Quintile 4","Quintile 5", "Quintile miss", "Subjetive status", 
                              "Subjetive upward mobility", "Supjetive downward mobility" ,"Subjetive non-mobility","Gender", "Age", "Meritorcatic perception", 
                              "Meritocratic preferences", "Unmeritocratic perception", "Unmeritocratic preferences", "Gini index", "Economic freedom index", 
                              "Merit-perception x Gini", "Merit-perception x Economic-freedom"))
```

@@

>>>>

htmlreg(list(results_0_redist,results_0_accum), 
        caption = "null model of Redistributive preferences and accumulation preferences", 
        custom.model.names = c("Redistributive", "Accumulation"), 
        caption.adove = T, star.symbol = "\\*")

@@

```{r results='asis'} 
htmlreg(list(results_1_redist__1, results_1_redist_3,results_1_redist_4,results_1_redist_5,results_1_redist_6,results_1_redist_7, results_1_redist_9, results_2_redist_macro_bv, results_3_redist_macro_bvi),
        caption = "Redistributive preference models", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "GINI x Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

@@

```{r results='asis'}
htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_nocong, results_3_accum_macro_bvi, results_3_accum_macro_bvi_nocong), 
        caption = "Comparison model excludig countries non convergent in the measurement", 
        custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), 
        custom.header = list("Redistributive" = 1:2, "Accumulation" = 3:4), 
        star.symbol = "\\*", 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> countries non convergent in the measurement model:Venezuela, Croatia, Cyprus, Italy, Latvia", 
        custom.coef.names = c("Intercept", "University. Ed.", "Quintile 2", "Quintile 3", "Quintile 4","Quintile 5", "Quintile miss", "Subjetive status", 
                              "Subjetive upward mobility", "Supjetive downward mobility","Subjetive non-mobility","Gender", "Age", "Meritorcatic perception", 
                              "Meritocratic preferences", "Unmeritocratic perception", "Unmeritocratic preferences", "Gini index", "Economic freedom index", 
                              "Merit-perception x Gini", "Merit-perception x Economic-freedom"), 
        caption.above = T)
```

@@

plota <- plot(estex.m23_2a, which="cook",
              cutoff = .1, sort = TRUE,
              xlab = "Cooks Distance Redistributive Model",
              ylab="Contries")

@@

```{r results='asis'}
htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_sininf,results_3_accum_macro_bvi, results_3_accum_macro_bvi_sininfl), 
        caption = "Comparison model Without influential cases in level two", 
        custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), 
        custom.header = list("Redistributive" = 1:2, "Accumulation" = 3:4), 
        caption.above = T, 
        star.symbol = "\\*", 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Influential contries: CYP, TUR, TWN, UKR,CZE, FRA, AUS, DNK, USA, VEN,PHL, POL, CHN, ISR, CHL, LVA, PHL", 
        custom.coef.names = c("Intercept", "University. Ed.", "Quintile 2", "Quintile 3", "Quintile 4","Quintile 5", "Quintile miss", "Subjetive status", 
                              "Subjetive upward mobility", "Supjetive downward mobility" ,"Subjetive non-mobility","Gender", "Age", "Meritorcatic perception", 
                              "Meritocratic preferences", "Unmeritocratic perception", "Unmeritocratic preferences", "Gini index", "Economic freedom index", 
                              "Merit-perception x Gini", "Merit-perception x Economic-freedom"))
```

@@

## Centrado

### Redistributive prefereneces centered on the group mean

```{r}

mer_pref$merit_g = as.numeric(mer_pref$merit - mer_pref$j_merit)
mer_pref$bmerit_g = as.numeric(mer_pref$bmerit - mer_pref$j_bmerit)
mer_pref$unmerit_g = as.numeric(mer_pref$unmerit - mer_pref$j_unmerit)
mer_pref$need_g = as.numeric(mer_pref$need - mer_pref$j_need)

results_1_redist__1  = lmer(redist ~  gini_neto + fi_index + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_redist_3 = lmer(redist ~ merit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_4 = lmer(redist ~  merit_g + bmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_5 = lmer(redist ~  merit_g + bmerit_g + unmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_6 = lmer(redist ~ merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_7 = lmer(redist ~ merit_g + fi_index + merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_9 = lmer(redist ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)
results_2_redist_macro_bv = lmer(redist ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + gini_neto + fi_index + 1 +  (1 + merit| v5c), data= mer_pref, REML=F)
results_3_redist_macro_bvi = lmer(redist ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + merit_g*gini_neto + fi_index + 1 +  (1 + merit_g | v5c), data = mer_pref, REML=F)

```

```{r results='asis'} 
htmlreg(list(results_1_redist__1, results_1_redist_3,results_1_redist_4,results_1_redist_5,results_1_redist_6,results_1_redist_7, results_1_redist_9, results_2_redist_macro_bv, results_3_redist_macro_bvi),
        caption = "Redistributive preference models centered on the group mean", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "GINI x Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

### Accumulation models centered on the group mean

```{r results='asis', cache=TRUE}
results_1_accum__1  = lmer(accum ~  gini_neto + fi_index + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum__2  = lmer(accum ~  gini_neto + fi_index + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum_3 = lmer(accum ~ merit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_4 = lmer(accum ~  merit_g + bmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_5 = lmer(accum ~ merit_g + bmerit_g + unmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_6 = lmer(accum ~ merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_7 = lmer(accum ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_8 = lmer(accum ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_9 = lmer(accum ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_macro = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + gini_neto + fi_index + 1 +  (1| v5c), data = mer_pref, REML=F)
results_2_accum_macro_bv = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  gini_neto + fi_index + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)
results_3_accum_macro_bvi = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  gini_neto + merit_g*fi_index + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)
results_3_accum_macro_bvi_2 = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  fi_index + merit_g*gini_neto + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)

```{r, results='asis'}
htmlreg(list(results_1_accum__1,results_1_accum__2, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), 
        caption = "Accumulation preferences models centered on the group mean", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Economic-freedom Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```
